SEDONA: A Novel Protocol for Identifying Infrequent, Long-Running Daemons on a Linux System

### 2017-04-07 sedona-ieice16/final/paper.tex
SEDONA finalization

\begin{summary}
Measuring program execution time is 
a \hbox{much-used} technique for performance evaluation in computer science. 
Without proper care, however, timed results may vary a lot, 
thus making it hard to trust their validity. 
In this paper we propose a novel timing protocol to significantly 
reduce such variability.

@@

\section{Introduction}
\label{sec:intro}

@@

{\color{blue}
Fig.~\ref{fig:synprog_test} compared the performance of 
the existing timing scheme, termed {\em ORG} using \hbox{end-to-end} (elapsed) time 
and our timing protocol, termed {\em \hbox{SEDONA}} 
(\hbox{Selective} Elimination through Detection of infrequent, \hbox{lOng-ruNning} dAemons), 
to be proposed shortly. 
For this comparison we used 
two kinds of real-world programs such as insertion sort, termed SORT and 
matrix multiplication (in column major), termed MM. 
As illustrated in Fig.~\ref{fig:synprog_test}, 
SEDONA outperformed ORG with regard to measurement quality by standard deviation. 
To be more specific, we observed that as workload size increased the performance gap between the two methods 
was increasingly bigger, reaching up to by six~times. 
}

\begin{figure}[t]
	\centering
	\subfigure[SORT - Standard Deviation]{
		\includegraphics[scale=0.31]{sort_std.eps}
		\label{fig:sort_std}
	}
	\subfigure[MM - Standard Deviation]{
		\includegraphics[scale=0.31]{matc_std.eps}
		\label{fig:matc_std}
	}
	%\vspace{-.1in}
	\caption{Performance Comparison on Real-world Programs~\label{fig:synprog_test}}
\vspace{-.3in}
\end{figure}

\vspace{-0.15in}
{\bf Characteristics.} There are several important specifics of our protocol. 
First, we utilize {\em process time} (PT) rather than on elapsed time (ET). 
The use of PT is preferred, as it takes into account 
the time taken for only a ``process'' (or program) of interest.
PT is defined as the sum of ticks (where one tick is equal to 10 msec)
in user and system mode. 
These tick measures are obtainable via {\tt taskstats} C struct, 
provided by the Linux NetLink facility~\cite{Netlink}. 
Second, the protocol throws out some executions that involve
{\em infrequent, \hbox{long-running} daemon processes}. 
We witness that such daemon processes substantially impact 
the execution time of the process.  
By eliminating those executions, the protocol greatly improves
the overall measurement quality, which would otherwise be biased by them.

@@

%\vspace{0.02in}
{\bf Contribution.} 
Our contributions are following.
\vspace{-0.1in}
\begin{itemize}

@@

\item The evaluation results on real-world programs 
show a support for the effectiveness of the protocol. 
}

\end{itemize}
\vspace{-0.2in}

\noindent
The rest is organized as follows. 
We next elaborate on the proposed timing protocol. In turn we evaluate the performance of the scheme using real workloads.

@@

{\bf Determining the Cutoffs}
Step~B consists of eight sub-steps, resulting in determining 
the cutoffs for each identified infrequent, long-running daemon.

@@

As already mentioned in Section~\ref{sec:intro}, we first 
confirmed the validity of our protocol with two 
real \hbox{CPU-bound} programs---insertion sort and \hbox{column-major} matrix multiplication---with heavy memory references.

To further assess the performance of the protocol, 
we proceeded with SPEC CPU2006 benchmarks~\cite{specCpu2006}, providing various 
\hbox{compute-bound} real applications.
%The results are \hbox{provided} in Table~\ref{tab:spec_real}. 
%Note that in the table the results for {\tt 481} and {\tt 483} \hbox{benchmarks} 
%are omitted because of some runtime error and incurred I/O, respectively.
Note that in this evaluation we could not obtain the results for {\tt 481} and {\tt 483} \hbox{benchmarks}. 
{\tt 481} threw some runtime error that we could not resolve, and {\tt 483} incurred I/O, which was out of scope of this article.
Hence, those two results are omitted in Table~\ref{tab:spec_real}.

Consequently, we reaffirmed from Table~\ref{tab:spec_real} that \hbox{SEDONA} bettered ORG,
on the standard deviation and relative error across the very different SPEC benchmarks.
Specifically, all the benchmarks revealed a smaller standard deviation 
from SEDONA as compared to that of ORG.
Our timing protocol quite effectively filtered out infrequent daemon executions 
in the industrial workloads. The relative error of SEDONA was also 
lower than that of ORG for almost every benchmark.
Roughly a 10x margin between the two schemes resulted from the {\tt 434} benchmark, for instance.
}

>>>>

\begin{summary}
Measuring program execution time is 
a \hbox{much-used} technique for performance evaluation in computer science. 
Without proper care, however, timed results may vary a lot, 
thus making it hard to trust their validity. 
{\color{blue}We propose a novel timing protocol to significantly 
reduce such variability by eliminating executions involving infrequent, \hbox{long-running} daemons.}

@@

\vspace{-0.05in}

\section{Introduction}
\label{sec:intro}
\vspace{-0.05in}

@@

{\color{blue}
Fig.~\ref{fig:synprog_test} compares the performance of 
the existing timing scheme, termed {\em ORG}, using elapsed time and our timing protocol, termed {\em \hbox{SEDONA}} 
(\hbox{Selective} \hbox{Elimination} through Detection of infrequent, \hbox{lOng-ruNning} dAemons), 
to be proposed shortly. 
For this comparison we used 
two kinds of real-world programs, specifically insertion sort, termed SORT and 
matrix multiplication (in column major), termed MM. 
As illustrated in Fig.~\ref{fig:synprog_test}, 
SEDONA outperformed ORG with regard to measurement quality by standard deviation. 
To be more specific, we observed that as workload size increased the performance gap between the two methods also increased, 
reaching up to by six~times. 
}

\begin{figure}[t]
	\centering
	\subfigure[SORT - Standard Deviation]{
		\includegraphics[scale=0.31]{sort_std.eps}
		\label{fig:sort_std}
	}
	\subfigure[MM - Standard Deviation]{
		\includegraphics[scale=0.31]{matc_std.eps}
		\label{fig:matc_std}
	}
	\vspace{-.15in}
	\caption{Performance Comparison on Real-world Programs~\label{fig:synprog_test}}
\vspace{-.25in}
\end{figure}

%\vspace{-0.15in}
{\bf Characteristics.} There are several important specifics of our protocol. 
First, we utilize {\em process time} (PT) rather than on elapsed time (ET). 
The use of PT is preferred, as it takes into account 
the time taken for only a ``process'' (or program) of interest.
PT is defined as the sum of ticks (where one tick is equal to 10 msec)
in user and system mode. 
These tick measures are obtainable via {\tt taskstats} C struct, 
provided by the Linux NetLink facility~\cite{Netlink}. 
Second, the protocol throws out some executions that involve
{\em infrequent, \hbox{long-running} daemon processes}. 
We witness that such daemon processes substantially impact 
the execution time of the process.  
By eliminating those executions, the protocol greatly improves
the overall measurement quality, which would otherwise be biased by them.

@@

%\vspace{0.02in}
{\bf Contribution.} 
Our contributions are following.
\vspace{-0.05in}
\begin{itemize}

@@

\item An evaluation on real-world programs 
shows a support for the effectiveness of the protocol. 
}

\end{itemize}
\vspace{-0.05in}

\noindent
The rest is organized as follows. 
We next elaborate on the proposed timing protocol. 
{\color{blue}In turn we assess the performance of the protocol using a popular industrial benchmark suite. 
%Finally, we conclude this letter by summarizing our discussion on the proposed protocol.}
Finally, we summarize our discussion.}

@@

{\bf Determining the Cutoffs.}
Step~B consists of eight sub-steps, resulting in determining 
the cutoffs for each identified infrequent, long-running daemon.

@@

As already seen in Figure~\ref{fig:synprog_test}, we 
confirmed the validity of our protocol with two 
real \hbox{CPU-bound} programs---insertion sort and \hbox{column-major} matrix multiplication---with heavy memory references.

To assess the performance of the protocol, 
we proceeded with SPEC CPU2006 benchmarks~\cite{specCpu2006}, providing various 
\hbox{compute-bound} real applications.
%The results are \hbox{provided} in Table~\ref{tab:spec_real}. 
%Note that in the table the results for {\tt 481} and {\tt 483} \hbox{benchmarks} 
%are omitted because of some runtime error and incurred I/O, respectively.
Note that in this evaluation we could not obtain the results for {\tt 481} and {\tt 483} \hbox{benchmarks}. 
{\tt 481} threw some runtime error that we could not resolve, and {\tt 483} incurred I/O, which was out of scope of this article.
Hence, those two results are omitted in Table~\ref{tab:spec_real}.

Consequently, we affirmed from Table~\ref{tab:spec_real} that \hbox{SEDONA} bettered ORG,
on the standard deviation and relative error across the very different SPEC benchmarks.
Specifically, all the benchmarks revealed a smaller standard deviation 
from SEDONA as compared to that of ORG.
Our timing protocol quite effectively filtered out infrequent daemon executions 
in the industrial workloads. The relative error of SEDONA was also 
lower than that of ORG for almost every benchmark.
Roughly a 10x margin between the two schemes resulted from the {\tt 434} benchmark, for instance.
}
